Robotic Grasping in Clutter: Using a Hierarchy of Supervisors with Learning from Demonstrations

### 2016-03-19 paper.tex
Edit pass.

\begin{abstract}
For applications such as Amazon warehouse order fulfillment, robots must grasp a desired object amid clutter: other objects that block direct access.  This can be difficult to program explicitly due to uncertainty in friction and push mechanics and the large number of objects that can be encountered. Online Learning from Demonstration (LfD) algorithms such as DAgger and SHIV have potential to learn robot control policies for tasks where the system dynamics and the cost function are unknown. To reduce the burden on human experts to provide control demonstrations, we propose using a hierarchy of supervisors and a Deep Learning network to learn a grasping in clutter task.  We consider 3 levels of supervisor, a fast motion planner that ignores obstacles, crowdsourced human workers who
provide appropriate robot control values via online videos, and local human experts.  Experiments suggest that we can leverage a hiearchy of supervisors to obtain 22,000 examples and achieve 80\% success on a held out test set of unknown objects.

@@

\begin{figure}
\includegraphics[width=0.5\textwidth]{f_figs/teaser.eps}
\caption{
Three roll-outs on a Zymark 3-DOF Robot of a fully trained grasping in clutter policy (one per column, top to bottom) which was trained using a
hierarchy of three supervisors consisting of an analytical motion planning, crowd-sourcing and human expert. 
Red shapes indicate clutter objects and the robot is trained to reach the yellow circle. The trained manipulation policy is represented as a deep neural network that recieves as input an image of the scene and outputs a change in state position. The resulting policy learns to sweep away clutter objects and reach the goal object. }
\vspace*{-20pt}
\label{fig:teaser}
\end{figure}

@@

Our approach is based on online Learning from Demonstrations (LfD) where a robot iteratively learns a policy and is
provided by feedback on the current policy roll out by a supervisor~\cite{grollman2007dogged,ross2010efficient,ross2010reduction}. 
We build on, DAgger, an online LfD algorithm which at each iteration, computes a policy based on prior demonstrations,
and then rolls out that policy. A supervisor then provides control signals as feedback on the current policy
and new state/control examples are aggregated with the prior examples for the next iteration. DAgger and related algorithms have been applied in a wide range of applications, from quadrotor flight to natural language to Atari games~\cite{NIPS2014_5421,duvallet2013imitation,ross2013learning}. 
Ross et al. showed that DAgger, under a no-regret assumption, can be guaranteed to deviate from the supervisor's policy with an error
at most linear in the time horizon for the task~\cite{ross2010reduction}.

One drawback is that DAgger imposes a substantial burden on the supervisor, who must label all states that the robot
visits during training.  Traditionally there has only been one supervisor and it is deemed an expert
~\cite{ross2010efficient,ross2010reduction,ross2013learning,duvallet2013imitation}. In this work, we propose to instead
utilize a hierarchy of supervisors that exhibit increasing cost and competence at a given task to incrementally
bootstrap the learning process.

In particular, while model-based planners might not yet capture the full physical interaction among all objects, it can be wasteful to not leverage them and learn with an expert supervisor from scratch. Thus, at the lowest level of the hierarchy, we use a motion planner on an relaxed version of the problem. In our grasping application, we use a planner that ignores the obstacles but can leverage knowledge of the kinematics and the goal.
The next supervisor in the hierarchy are crowdsource workers on Amazan Mechnical Turk. Then finally the robot is trained with a Phd student in robotics, who is an expert human supervisor. Examples of the resulting learned grasping in clutter policy can be seen in Fig. \ref{fig:teaser}.

@@

\section{Related Work}
Below, we summarize related work in Robotic Grasiping in Clutter, the Online LfD setting and then the field of
Curriculum learning, which is related to the concept of hierarchical supervisors.

\noindent \textbf{Robotic Grasping in Clutter}
Robotic grasping is a well-established research topic in robotics that has been studied for several
decades~\cite{bicchi2000robotic}. A significant amount of prior work focuses on planning grasps given a known object.
However, in unstructured environments clutter poses a significant challenge for reaching the planned grasp
~\cite{katz2008can}. Prior work has addressed integrated perception and grasping in clutter where the objective is to
grasp objects in an unorganized pile ~\cite{pinto2015supersizing,nieuwenhuisen2013mobile}, but these methods do not
specifically aim to grasp a single target object in clutter.

However, prior work has studied the problem of manipulating objects
by performing pushing operations~\cite{mason1986mechanics}.  Cosgun et al.~\cite{cosgun2011push} and King et al. \cite{kingnonprehensile} consider the problem of planning
a series of push operations that move an object to a
desired target location. Kiteav et al. planned a trajectory in a physics simulator using LQG based controllers
\cite{kitaevphysics}. However, all of these works assume known properties of the object model, such as mass and friction coefficient  or access to an object model in a physics simulator, which could be difficult to obtain for unknown objects.

Leeper et al. ~\cite{leeper2012strategies} used a human operator for assistance
to guide the robot through clutter with the objective of grasping a target object. However, the robot required the human
to be present at all times and did not attempt to learn to operate autonomously. We are interested in a data-driven
approach that only queries a supervisor at training time and  can operate autonomously thereafter.

A learning model-free based approach to robotic manipulation is Guided Policy Search~\cite{levine2015end}. However, this assumes a known low-dimensional state representation to both estimate dynamics and perform LQG in. In the grasping in clutter domain, it can be hard to specify such a low dimensional representation due the dependence on the objects' shape when planning a pushing strategy.

\noindent \textbf{Online Lfd with an Expert Supervisor}
Successful robotic examples of Online Learning From Demonstration with an expert supervisor include applications to flying a quad-copter through a forest, navigating a wheel chair across a room and teaching a robot to follow verbal instructions and surgical needle insertion \cite{ross2013learning, kim2013maximum, duvallet2013imitation, laskeyshiv}.

However, to date, these approaches have used only one expert supervisor to provide training data for all parts of the
state space. We propose to instead utilize hierarchy of supervisor of different skill level and cost to reduce the
overall learning cost.

\noindent\textbf{Reducing Supervisor Burden in Online LfD} One approach that has been studied to reduce the number of
supervisor supervision is to apply active learning to only ask for supervision when the robot is uncertain about the
correct control to apply. Traditional active learning techniques like query-by-committee and uncertainty sampling have
in particular be utilized for this purpose \cite{chernova2009interactive,judah2011active,grollman2007dogged}

However, Kim et al. demonstrated that due to the non-stationarity of the distribution of states encountered during
learning, the traditional active learning techniques may be suitable since the underlying state distribution changes.
Thus the use of novelty detection was proposed~\cite{kim2013maximum}. Laskey et al. introduced SHIV, using an active
learning approach tailored to high dimensional and non-stationarity state distributions and a modified version of the
One Class SVM classifier. This enabled the authors to reduce the density estimation problem to a 
simpler regularized binary classification~\cite{laskeyshiv}. However the grasping in clutter problem exhibits a high amount
of stochasticity requiring a large training data set which poses a significant computational challenge to these methods.
In the present paper, we hence consider using Deep Learning, as an underlying scalable learning algorithm in combination
with DAgger.

\noindent\textbf{Curriculum Learning}
Our approach is closely related to ideas from curriculum learning, where a neural network is trained via 
incrementally, first on easier examples and then gradually on data of increasing difficulty~\cite{bengio2009curriculum}.

Sanger et al. used curriculum learning in robotics to gradually train a neural network policy to learn the inverse
dynamics of a robot manipulator. They then considered a collection scheme where easily learned trajectories where shown
to the robot first and then gradually increased the difficulty~\cite{sanger1994neural}.

Our approach is different from curriculum learning, which assumes all training data presented to the neural network is valid.  We  instead train on a completely different set of examples throughout the supervisor hierarchy.  In these different set of examples, some could be very low-quality examples and will enforce a behavior that needs to be retrain with a more-skilled supervisor.

@@

\noindent\textbf{Assumptions and Modeling Choices } 
We assume a known state space and set of controls. We also assume access to a robot or simulator, such that we  can sample from the state sequences induced by a sequence of controls.Lastly, we assume access to a set of supervisors who can, given a state, provide a control signal label. We additionally assume the supervisors can be noisy and imperfect, noting that a lower cost supervisor also has lower quality.

@@

\noindent\textbf{Policies and State Densities.}
Following conventions from control theory, we denote by $\mathcal{X}$ the set of observable states for a robot task, consisting, for example, of 
high-dimensional vectors corresponding to images from a camera, or robot joint angles and object poses in the environment.
We denote by $\mathcal{U}$ the set of allowable control inputs for the robot. $\mathcal{U}$ may be discrete or
continuous in nature. We model dynamics as Markovian: the probability of state $\mathbf{x_{t+1}}\in
\mathcal{X}$ depends only oni the previous state $\mathbf{x}_t\in\mathcal{X}$ and control input $\mathbf{u}_t\in
\mathcal{U}$: 
$$p(\bx_{t+1}|\bu_{t},\bx_{t}, \ldots, \bu_{0}, \bx_{0})=p(\bx_{t+1}|\bu_{t}, \bx_t)$$
We assume an unknown probability density over initial states $p(\bx_0)$.

A demonstration (or trajectory) $\hat{\tau}$ is a series of $T+1$ pairs of states visited and corresponding
control inputs at these states, $\hat{\tau} = (\mathbf{x}_0,\mathbf{u}_0, ...., \mathbf{x}_T,\mathbf{u}_T)$, where $\bx_t\in \mathcal{X}$
and $\bu_t\in \mathcal{U}$ for $t\in \{0, \ldots, T\}$ and some $T\in \mathbb{N}$.  
For a given trajectory $\hat{\tau}$ as above, we denote by ${\tau}$ the corresponding trajectory in state space,
${\tau} = (\bx_0,....,\bx_T)$.

@@

While we do not assume knowledge of the distributions corresponding to: $p(\bx_{t+1}|\bx_t,\bu_t)$, $p(\bx_0)$, $p(\bx_t|
\theta)$ or $p(\bx|\theta)$, we assume that we have a stochastic robot or a simulator such that for any state
$\bx_t$ and control $\bu_t$, we can sample the $\bx_{t+1}$ from the density $p(\bx_{t+1}|\pi_{\theta}(\bx_t),\bx_t)$. 
Therefore, 'rolling out' trajectories under a policy
$\pi_{\theta}$ in our experiments, we utilize the robot to sample the resulting stochastic trajectories rather than
estimating $p(\bx|\theta)$ itself.

@@

Given a candidate policy $\pi_{\theta}$, we DAgger uses the surrogate loss function to approximately measure how `close' the robot's policy's
returned control input $\pi_{\theta}(\bx)\in \mathcal{U}$ at a given state $\bx\in \mathcal{X}$ is to the supervisor's policy's control output
$\tilde{\pi}(\bx)\in \mathcal{U}$. The goal is of DAgger is to produce a policy that minimizes the expected surrogate loss:

@@

 In particular, this paper provides an empirical study of greedy, with respect to cost, combinations of three types of supervisors $S_1,
S_2, S_3$ for grasping in clutter which are applied in order to train a policy parameterized by a deep neural network.
Here, $S_1$ is an analytical motion planning algorithm with a cost $C_1=0.01$, $S_2$ a supervisor
consisting a crowd-sourced Amazon Mechanical Turk laborers with $C_2=0.1$, and $S_3$ a human expert supervisor with
$C_3=1$.

\section{Approach and Background}
 \subsection{Details on DAgger: Dataset Aggregation}
Since the cumulative expected reward of a policy is difficult to optimize directly,
DAgger~\cite{ross2010reduction} instead solves the minimization in Eq. \ref{eq:LFD_obj} by iterating two steps: 1)
computing the policy parameter $\theta$ using the training data $\mathcal{D}$ thus far, and 2) execute the policy induced by the current $\theta$, and ask for labels for the encountered states.

@@

This sub-problem is a supervised learning problem, solvable by estimators like a support vector machine or a neural net. Performance can vary though with the selection of a the estimator~ Selecting the correct function class depends on the task being consider and knowledge of the problem, see for a guide~\cite{scholkopf2002learning}.

 \subsubsection{Step 2}
The second step  DAgger rolls out their policies, $\pi_{\theta_{k}}$, to sample states that are likely under $p(\bx|\theta_{k})$.  For every state visited, DAgger requests the supervisor to provide the appropriate control/label. Formally, for a given sampled trajectory  $\hat{\tau} = (\bx_0,\bu_0,...,\bx_T,\bu_T )$, the supervisor provides labels $\tilde{\bu}_t$, where $\tilde{\bu}_t \sim \tilde{\pi}(\bx_t) + \epsilon$, where $\epsilon$ is a small zero mean noise term, for $t\in \{0, \ldots, T\}$.
The states and labeled controls are then aggregated into the next data set of demonstrations $\mathcal{D}_{k+1}$:
$$D_{k+1}=\mathcal{D}_k \cup \{(\bx_t,\tilde{\bu_t})\|t\in\{0,\ldots,T\}\} $$

%\fpnote{terms such as aggregated etc would be much clearer if we just refer to a particular line in the algorithm}

Steps 1 and 2 are repeated for $K$ iterations or until 
the robot has achieved sufficient performance on the task\footnote{In the original DAgger the policy rolled out
was stochastically mixed with the supervisor, thus with probability $\beta$ it would either take the supervisor's action
or the robots. The use of this stochastically mix policy was for theoretical analysis. In practice, it is recommended
to set $\beta = 0$ to avoid biasing the sampling~\cite{NIPS2014_5421,ross2010reduction}}.

@@

While one could consider to learn a policy using model-free reinforcement learning algorithms
~\cite{sutton1998reinforcement}, where a selection strategy will query different supervisors and learn over time the
best supervisor to select given the current policy, this approach requires substantial numbers of 
queries for supervision of the costliest supervisor at each iteration. In light of this, we propose a greedy allocation
strategy with respect the cost of the supervisor.

@@

While for large numbers of iterations, convergence tests can be applied to determine a point of diminishing return at
which a switch to the next supervisor in the hierarchy can be initiated, this approach can be challenging when only a
limited numbers of roll-outs can be afforded. In practice, we either advanced when the surrogate loss between
supervisors was sufficiently low or when the performance on the grasping in clutter task was not improving empirically. 
For crowdsourcing in particular, we chose the second option since, due to the large variance between demonstrations
we were not able to determine a fixed threshold for the surrogate loss. We hope to significantly scale the number of
training steps in future work to investigate various switching criterea in full detail.

\section{Robot Grasping in Clutter}
Let us now describe how we apply the above approach for the grasping in clutter problem. We consider a robot grasping an
object in a cluttered environment. The robot's goal is to grasp a yellow cylindrical target object while other extruded
planar objects obstruct the path towards the goal object. Since contact dynamics are difficult to model \cite{kitaevphysics,kingnonprehensile}, we do not assume the knowledge of explicit object or dynamics models and instead learn a grasping policy directly from labeled
overhead video data. The state space space $\mathcal{X}$, is hence given by an image from an overhead video
camera, observing a set of K objects, the robot arm and a goal object in a bounded workspace. As the underlying reward
function, or $r: \mathcal{X}\times \mathcal{U} \rightarrow \lbrace 0, 1\rbrace$, where $U$ denotes continuous control
signals given by delta values of joint angles. We consider the following three supervisors $S_1, S_2, S_3$.

@@

\noindent \textbf{CrowdSourced Supervisor} The second supervisor, $S_2$, relies on a crowd source service, called Amazon
Mechanical Turk (AMT). The AMT platform makes readily available thousands of human workers that we can query to provide robot
supervision examples for approximately \$0.1 per robot trial. 
We designed the supervision interface shown in Fig. \ref{fig:overlays}. The interface displays a video of a roll-out of
the current robot policy and allows the human supervisors to command an overlay visualization of the robot arm to
showcase a deviation to the current policy that should be applied with a maximal angle joint deviation of 15 degree and maximal extension deviation of 1cm  to
the current roll-out.

We additionally designed a tutorial for the CrowdSourced Supervisor. We first desribe the learning task to them as a
robot that is trying to reach a yellow cynlider and needs their help learning how to get it. In a tutorial, they are then trained
to perform designated motions with a virtual robot, to help them understand how the robot's kinematics. We additionally
provide a video of an expert providing corrections on three robot trajectories. We lastly instruct the CrowdSourced
Supervisor to only label when they are sure in their decision, in order to minimize contradictory examples associated
with random guesses.

To help ensure quality, we provide all CrowdSourced Supervisors with the same robot trial first and measure their
performance against the performance of a Human Expert Supervisor. If the average Squared-Euclidean distance over control
signals between examples is above a threshold, then the Crowdsource Supervisor is not asked to provide additional examples.

\noindent \textbf{Human Expert Supervisor} The final supervisor, $S_3$ is the Human Expert supervisor, who is capable of
achieving high cumulative reward but is a limited resource. An Human Expert Supervisor in this case is a Phd student in
machine learning and robotics, to which we assign a cost of $C_3=1.0$. The Human Expert Supervisor uses the same
interface as the CrowdSourced supervisors, shown in Fig. \ref{fig:overlays}, to provide examples to the robot.

@@

\caption{\footnotesize Example of how the binary mask applied to each RGB channel affects the input data. As you can see it reduces the dimensionality of each channel's pixel value from the range of [0,255] to [0,1], which can allow for less data needed during learning and robustness to small lighting conditions.  }

@@

\caption{\footnotesize  Shown above is a Zymark robot. The robot consists of an 3DOF arm that lies in a planar workspace. It is able to extend its arm and rotate about a fixed base. The robot can also open and close its gripper.}

@@

\caption{\footnotesize  The set of objects that the robot was trained on. The Training objects on the right are the four objects used in training. The test objects on the left represent represent objects that were found in our test configurations. The test objects vary in size and shape from the training objects, which can test how well the robot learns to manipulate unknown objects. Every test configuration contained at least one object from this set to guarantee it wasn't trained on.  }

@@

\caption{\footnotesize  On the right is examples of training configurations we presented to the robot. The shapes were arranged around the goal object in different poses and in different parts of the workspace. At testing time, we had similar configurations but some shapes were unknown objects that were not trained on. }
\vspace*{-20pt}
\label{fig:suc_meas}
\end{figure}

We discuss our experimental setup and test the performance of using a supervisor hierarchy versus a baseline approach
with one supervisor. We then evaluate the quality the CrowdSource supervisors.

>>>>

\begin{abstract}
For applications such as Amazon warehouse order fulfillment, robots must grasp a desired object amid clutter: other
objects that block direct access.  This can be difficult to program explicitly due to uncertainty in friction and push
mechanics and the large number of objects that can be encountered. Online Learning from Demonstration (LfD) algorithms
such as DAgger and SHIV have potential to learn robot control policies for tasks where the system dynamics and the cost
function are unknown. To reduce the burden on human experts to provide control demonstrations, we propose using a
hierarchy of supervisors and a Deep Learning network to learn a grasping in clutter task.  We consider 3 levels of
supervisors, a fast motion planner that ignores obstacles, crowdsourced human workers who
provide appropriate robot control values via online videos, and local human experts.  Experiments suggest that we can
leverage a hiearchy of supervisors to obtain 22,000 labelled training data examples and achieve 80\% success on a held out test set of unknown objects.

@@

\begin{figure}
\includegraphics[width=0.5\textwidth]{f_figs/teaser.eps}
\caption{
    \footnotesize
Three policy roll-outs on a Zymark 3-DOF Robot of a fully trained grasping in clutter policy (one per column, top to
bottom) which was trained using a hierarchy of three supervisors consisting of a motion planning algorithm, crowd-sourcing and a human expert. 
Red shapes indicate clutter objects and the robot is trained to reach the yellow cylinder. The trained manipulation
policy is represented as a deep neural network that recieves as input an image of the scene and outputs a change in
state position. The resulting policy learns to sweep away clutter objects to reach the goal object. }
\vspace*{-20pt}
\label{fig:teaser}
\end{figure}

@@

Our approach is based on Online Learning from Demonstrations where a robot iteratively learns a policy and is
provided feedback on the current policy roll out by a supervisor~\cite{grollman2007dogged,ross2010efficient,ross2010reduction}. 
We build on, DAgger, an online LfD algorithm which at each iteration, computes a policy based on prior demonstrations,
and then rolls out that policy. A supervisor then provides control signals as feedback on the current policy
and new state/control examples are aggregated with the prior examples for the next iteration. DAgger and related algorithms have been applied in a wide range of applications, from quadrotor flight to natural language to Atari games~\cite{NIPS2014_5421,duvallet2013imitation,ross2013learning}. 
Ross et al. showed that DAgger, under a no-regret assumption, can be guaranteed to deviate from the supervisor's policy with an error
at most linear in the time horizon for the task~\cite{ross2010reduction}.

One drawback is that DAgger imposes a substantial burden on the supervisor, who must label all states that the robot
visits during training.  Previously a single expert supervisor has been considered 
~\cite{ross2010efficient,ross2010reduction,ross2013learning,duvallet2013imitation}. In this work, we propose to instead
utilize a hierarchy of supervisors that exhibit increasing cost and competence at a given task to incrementally
bootstrap the learning process. In particular, while model-based planners might not capture physical interactions with
complete realism, we propose to leverage them in the initial training phase rather than to utilize an expensive
expert supervisor from scratch. Thus, at the lowest level of the hierarchy, we use a motion planner on an simplified
version of the grasping in clutter problem that ignores ambient obstacles. As the next supervisor in the hierarchy 
we consider crowdsourced workers on Amazan Mechnical Turk and finally the robot is trained with a Phd student in
robotics, who is considered an expert human supervisor. Examples of the resulting learned grasping in clutter policy can be seen in Fig. \ref{fig:teaser}.

@@

\section{Related Work}
Below, we summarize related work in Robotic Grasiping in Clutter, the Online LfD setting and Curriculum learning.

\noindent \textbf{Robotic Grasping in Clutter}
Robotic grasping is a well-established research topic in robotics that has been studied for several
decades~\cite{bicchi2000robotic}. A significant amount of prior work focuses on planning grasps given a known object.
However, in unstructured environments clutter poses a significant challenge for reaching the planned grasp
~\cite{katz2008can}. Prior work has addressed integrated perception and grasping in clutter where the objective is to
grasp objects in an unorganized pile~\cite{pinto2015supersizing,nieuwenhuisen2013mobile}, but these methods do not
specifically aim to grasp a single target object in clutter. 
Prior work has studied the problem of manipulating objects
by performing pushing operations~\cite{mason1986mechanics}.  Cosgun et al.~\cite{cosgun2011push} and King et al. \cite{kingnonprehensile} consider the problem of planning a series of push operations that move an object to a
desired target location. Kiteav et al. planned a trajectory in a physics simulator using LQG based controllers
\cite{kitaevphysics}. However, all of these works assume known properties of the object model, such as mass and friction
coefficient  or access to an object model in a physics simulator, which can be difficult to obtain for unknown objects. 
Leeper et al. ~\cite{leeper2012strategies} used a human operator for assistance
to guide the robot through clutter with the objective of grasping a target object. However, the robot required the human
to be present at all times and did not attempt to learn to operate autonomously. We are interested in a data-driven
approach that only queries a supervisor at training time and  can operate autonomously thereafter.

A model-free approach to robotic manipulation is Guided Policy Search~\cite{levine2015end}. However, this assumes a
known low-dimensional state representation to both estimate dynamics and perform LQG in. In the grasping in clutter
domain, it can be hard to specify such a low dimensional representation due the dependence on the objects' shape.

\noindent \textbf{Online LfD with an Expert Supervisor}
Successful robotic examples of Online Learning From Demonstration with an expert supervisor include applications to flying a quad-copter through a forest, navigating a wheel chair across a room and teaching a robot to follow verbal instructions and surgical needle insertion \cite{ross2013learning, kim2013maximum, duvallet2013imitation, laskeyshiv}. 
However, to date, these approaches have used only one expert supervisor to provide training data for all parts of the
state space. We propose to instead utilize hierarchy of supervisor of different skill level and cost to reduce the
overall learning cost.

\noindent\textbf{Reducing Supervisor Burden in Online LfD} 
Active learning approaches to reducing supervisor burden only ask for supervision when the robot is uncertain about the
correct control to apply. Traditional active learning techniques like query-by-committee and uncertainty sampling have
in particular be utilized for this purpose \cite{chernova2009interactive,judah2011active,grollman2007dogged}
Kim et al. demonstrated that due to the non-stationarity of the distribution of states encountered during
learning, the traditional active learning techniques may not be suitable.
Thus the use of novelty detection was proposed~\cite{kim2013maximum}. Laskey et al. introduced SHIV, using an active
learning approach tailored to high dimensional and non-stationarity state distributions and a modified version of the
One Class SVM classifier. This reduced the density estimation problem to a 
simpler regularized binary classification~\cite{laskeyshiv}. However the grasping in clutter problem exhibits a high amount
of variability in parameters requiring a large training data set. This poses a significant computational challenge to these methods.
In the present paper, we hence consider using Deep Learning, as a scalable learning algorithm in combination
with DAgger.

\noindent\textbf{Curriculum Learning}
Our approach is closely related to ideas from curriculum learning, where a neural network is trained  
incrementally, first on easier examples and then gradually on data of increasing difficulty~\cite{bengio2009curriculum}.
Sanger et al. used curriculum learning to gradually train a neural network policy to learn the inverse
dynamics of a robot manipulator. They then considered a collection scheme where easily learned trajectories where shown
to the robot first and then gradually increased the difficulty~\cite{sanger1994neural}.
We avoid the complexity of ranking training data by difficulty and instead propose an iterative scheme where
data is presented in an unbiased manner to a hierarchy of supervisors.

@@

\noindent\textbf{Assumptions and Modeling Choices } 
We assume a known state space and set of controls. We also assume access to a robot or simulator, such that we can sample from the state sequences induced by a sequence of controls. Lastly, we assume access to a set of supervisors who can, given a state, provide a control signal label. We additionally assume the supervisors can be noisy and imperfect, noting that a lower cost supervisor also has lower quality.

@@

\noindent\textbf{Policies and State Densities.}
We denote by $\mathcal{X}$ the set of observable states for a robot task, consisting, for example, of 
high-dimensional vectors corresponding to images from a camera, or robot joint angles and object poses in the environment.
We denote by $\mathcal{U}$ the set of allowable control inputs for the robot. $\mathcal{U}$ may be discrete or
continuous in nature. We model dynamics as Markovian: the probability of state $\mathbf{x_{t+1}}\in
\mathcal{X}$ depends only only the previous state $\mathbf{x}_t\in\mathcal{X}$ and control input $\mathbf{u}_t\in
\mathcal{U}$: 
$$p(\bx_{t+1}|\bu_{t},\bx_{t}, \ldots, \bu_{0}, \bx_{0})=p(\bx_{t+1}|\bu_{t}, \bx_t)$$
We assume an unknown probability density over initial states $p(\bx_0)$.
A demonstration (or trajectory) $\hat{\tau}$ is a series of $T+1$ pairs of states visited and corresponding
control inputs at these states, $\hat{\tau} = (\mathbf{x}_0,\mathbf{u}_0, ...., \mathbf{x}_T,\mathbf{u}_T)$, where $\bx_t\in \mathcal{X}$
and $\bu_t\in \mathcal{U}$ for $t\in \{0, \ldots, T\}$ and some $T\in \mathbb{N}$.  
For a given trajectory $\hat{\tau}$ as above, we denote by ${\tau}$ the corresponding trajectory in state space,
${\tau} = (\bx_0,....,\bx_T)$.

@@

While we do not assume knowledge of the distributions corresponding to: $p(\bx_{t+1}|\bx_t,\bu_t)$, $p(\bx_0)$, $p(\bx_t|
\theta)$ or $p(\bx|\theta)$, we assume that we have a stochastic robot or a simulator such that for any state
$\bx_t$ and control $\bu_t$, we can sample the $\bx_{t+1}$ from the density $p(\bx_{t+1}|\pi_{\theta}(\bx_t),\bx_t)$. 
Therefore, `rolling out' trajectories under a policy
$\pi_{\theta}$ in our experiments, we utilize the robot to sample the resulting stochastic trajectories rather than
estimating $p(\bx|\theta)$ itself.

@@

Given a candidate policy $\pi_{\theta}$, DAgger uses the surrogate loss function to approximately measure how `close' the robot's policy's
returned control input $\pi_{\theta}(\bx)\in \mathcal{U}$ at a given state $\bx\in \mathcal{X}$ is to the supervisor's policy's control output
$\tilde{\pi}(\bx)\in \mathcal{U}$. The goal is of DAgger is to produce a policy that minimizes the expected surrogate loss:

@@

In particular, this paper provides an empirical study of greedy (with respect to cost) combinations of three types of supervisors $S_1,
S_2, S_3$ for grasping in clutter which are applied in order to train a policy parameterized by a deep neural network.
Here, $S_1$ is an analytical motion planning algorithm with a cost $C_1=0.01$, $S_2$ a supervisor
consisting a crowd-sourced Amazon Mechanical Turk laborers with $C_2=0.1$, and $S_3$ a human expert supervisor with
$C_3=1$.

\section{Approach and Background}
 \subsection{Details on DAgger: Dataset Aggregation}
Since the cumulative expected reward of a policy is difficult to optimize directly,
DAgger~\cite{ross2010reduction} instead solves the minimization in Eq. \ref{eq:LFD_obj} by iterating two steps: 1)
computing the policy parameter $\theta$ using the training data $\mathcal{D}$ thus far, and 2) by executing the policy
induced by the current $\theta$, and asking for labels for the encountered states.

@@

This sub-problem is a supervised learning problem, which we solve with a deep neural network. Other approaches such as
support vector machines can also be considered~\cite{scholkopf2002learning}.

 \subsubsection{Step 2}
The second step at iteration $k$, DAgger rolls out the current policy, $\pi_{\theta_{k}}$, to sample states that are likely under $p(\bx|\theta_{k})$.  For every state visited, DAgger requests the supervisor to provide the appropriate control/label. Formally, for a given sampled trajectory  $\hat{\tau} = (\bx_0,\bu_0,...,\bx_T,\bu_T )$, the supervisor provides labels $\tilde{\bu}_t$, where $\tilde{\bu}_t \sim \tilde{\pi}(\bx_t) + \epsilon$, where $\epsilon$ is a small zero mean noise term, for $t\in \{0, \ldots, T\}$.
The states and labeled controls are then aggregated into the next data set of demonstrations $\mathcal{D}_{k+1}$:
$$D_{k+1}=\mathcal{D}_k \cup \{(\bx_t,\tilde{\bu_t})|t\in\{0,\ldots,T\}\} $$

Steps 1 and 2 are repeated for $K$ iterations or until the robot has achieved sufficient performance on the
task\footnote{In the original DAgger the policy rollout was stochastically mixed with the supervisor, thus with
    probability $\beta$ it would either take the supervisor's action or the robots. The use of this stochastically mix
    policy was for theoretical analysis and in practice, it was recommended to set $\beta = 0$ to avoid biasing the
sampling~\cite{NIPS2014_5421,ross2010reduction}}.

@@

While one could consider to learn a policy using model-free reinforcement learning algorithms~\cite{sutton1998reinforcement}, where a selection strategy will query different supervisors and learn over time the
best supervisor to select given the current policy, this approach requires substantial numbers of 
queries for supervision of the costliest supervisor at each iteration. In light of this, we propose a greedy allocation
strategy with respect the cost of the supervisor.

@@

While for large numbers of iterations, convergence tests can be applied to determine a point of diminishing return at
which a switch to the next supervisor in the hierarchy can be initiated, this approach can be challenging when only a
limited numbers of roll-outs can be afforded. In practice, we either advanced when the surrogate loss between
supervisors was sufficiently low or when the performance on the grasping in clutter task was not improving empirically. 
For crowdsourcing in particular, we chose the second option since, due to the large variance between demonstrations,
we were not able to determine a fixed supervisor switching threshold for the surrogate loss. We hope to significantly scale the number of
training steps in future work to investigate various switching criterea in full detail.

\section{Robot Grasping in Clutter}
Let us now describe how we apply the above approach for the grasping in clutter problem. We consider a robot grasping an
object in a cluttered environment. The robot's goal is to grasp a yellow cylindrical target object while other extruded
planar objects obstruct the path towards the goal object. Since contact dynamics are difficult to model \cite{kitaevphysics,kingnonprehensile}, we do not assume the knowledge of explicit object or dynamics models and instead learn a grasping policy directly from labeled
overhead video data. The state space space $\mathcal{X}$, is hence given by an image from an overhead video
camera, observing a set of K objects, the robot arm and a goal object in a bounded workspace. As the underlying reward
function, or $r: \mathcal{X}\times \mathcal{U} \rightarrow \lbrace 0, 1\rbrace$, where $U$ denotes continuous control
signals given by delta values of joint angles, we consider {\color{blue} [WHAT IS IT??]}. We consider the following three supervisors $S_1, S_2, S_3$.

@@

\noindent \textbf{Crowd-Sourced Supervisor} The second supervisor, $S_2$, relies on a crowd source service, called Amazon
Mechanical Turk (AMT). The AMT platform makes readily available thousands of human workers that we can query to provide robot
supervision examples for approximately \$0.1 per robot trial. 
We designed the supervision interface shown in Fig. \ref{fig:overlays}. The interface displays a video of a roll-out of
the current robot policy and allows the human supervisors to command an overlay visualization of the robot arm to
showcase a deviation to the current policy that should be applied with a maximal angle joint deviation of 15 degree and maximal extension deviation of 1cm  to
the current roll-out.

We additionally designed a tutorial for the Crowd-Sourced Supervisor. We first desribe the learning task to them as a
robot that is trying to reach a yellow cynlider and needs their help learning how to get it. In a tutorial, they are then trained
to perform designated motions with a virtual robot, to help them understand how the robot's kinematics. We additionally
provide a video of an expert providing corrections on three robot trajectories. We lastly instruct the Crowd-Sourced
Supervisor to only label when they are sure in their decision, in order to minimize contradictory examples associated
with random guesses.

To help ensure quality, we provide all Crowd-Sourced Supervisors with the same robot trial first and measure their
performance against the performance of a Human Expert Supervisor. If the average Squared-Euclidean distance over control
signals between examples is above a threshold, then the Crowdsource Supervisor is not asked to provide additional examples.

\noindent \textbf{Human Expert Supervisor} The final supervisor, $S_3$ is the Human Expert supervisor, who is capable of
achieving high cumulative reward but is a limited resource. An Human Expert Supervisor in this case is a Phd student in
machine learning and robotics, to which we assign a cost of $C_3=1.0$. The Human Expert Supervisor uses the same
interface as the Crowd-Sourced supervisors, shown in Fig. \ref{fig:overlays}, to provide examples to the robot.

@@

\caption{\footnotesize Example of how the binary mask applied to each RGB channel affects the input data. As can be seen
it reduces the range of each channel's pixel value from the range of [0,255] to [0,1], increasing robustness to small
lighting condition changes.  }

@@

\caption{\footnotesize  Shown above is a Zymark robot. The robot consists of an 3DOF arm in a planar workspace. It is able to extend its arm and rotate about a fixed base. The robot can also open and close its gripper.}

@@

\caption{\footnotesize  The Training objects on the right are the four objects used in training. The test objects on the
left represent represent objects that were added in our test configurations. Every test configuration contained at least
one of the objects on the right.}

@@

\caption{\footnotesize  Right: examples of training configurations we presented to the robot. The shapes were arranged
around the goal object in different poses and in different parts of the workspace. At test time, we considered similar configurations but 
added some unknown objects not present in the test set. }
\vspace*{-20pt}
\label{fig:suc_meas}
\end{figure}

We discuss our experimental setup and test the performance of using a supervisor hierarchy versus a baseline approach
with one supervisor. We then evaluate the quality the Crowd-Source supervisors.

\subsection{Experimental Setup}
We work with a Zymark robot to perform a grasping in clutter task. The robot, shown in Fig. \ref{fig:robot}, has a 3
dimensional internal state of base rotation, arm extension and gripper opening width. The robot is commanded via position 
control with a tuned PID controller. We used
relative state control because this enabled us to easily enforce stay out zones for safety
and to register control signals to the labeling interface in Fig. \ref{fig:overlays}. We utilize the two main rotational joints of the
robot as degrees of freedom which are controled by a neural network policy $\pi_{\theta}$ trained on image data taken by
an overhead Logitech C270 camera. Examples of images from the camera can be seen in Fig. \ref{fig:teaser}.

We consider objects made of Medium Density Fiberboard with an average 4" diameter. The objects used to form clutter are
painted red while the goal object is a yellow cylinder. The robot workspace consists of a disk region which is
surrounded by an elevated plate constraining the objects to the workspace and prohibiting them from being sweeped off
the workspace, thus adding to the difficulty of the task.
